---
title: "Assignment 2 - S17465"
author: "S17465"
date: '2023-07-27'
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Import Dataset

```{r}
library(readr)
library(CCA)
library(CCP)
library(candisc)
```

```{r}
df <- read.csv('E:/Uni Docs/4th year/1st Sem/ST405/Mini Project 2/wine.csv')
```

### Data Pre-Processing

```{r}
summary(df)
```

```{r}
library(dplyr)

# Check for null values in each column
missing_values <- df %>%
  summarise_all(~ sum(is.na(.)))

# Print the number of missing values in each column
print(missing_values)
```

```{r}
colnames(df)
```

Separate the 13 variables into two groups. The first group has 9 variables Alcohol, Malic_Acid,Ash,Ash_Alcanity,Magnesium,Total_Phenols,Flavanoids,Nonflavanoid_Phenols,Proanthocyanins. The second group has 4 variables Color_Intensity, Hue,OD280 and Proline.

```{r}
chemical_properties <- cbind(df[,1:9])
sensory_properties <- cbind(df[,10:13])
```

```{r}
chemical_properties
```

```{r}
sensory_properties
```

Standardize all variables and apply CCA . This function will transform each variable to have a mean of 0 and a standard deviation of 1, ensuring that all variables are on the same scale.

```{r}
library(dplyr)

chemical_properties_st <- chemical_properties %>%
  mutate(across(everything(), scale))

sensory_properties_st <- sensory_properties %>%
  mutate(across(everything(), scale))

```

```{r}
chemical_properties_st
```

```{r}
sensory_properties_st
```

```{r}
cp_mat <- as.matrix(chemical_properties_st)
sp_mat <- as.matrix(sensory_properties_st)
```

### Performing CCA

```{r}
cca_result <- cc(cp_mat,sp_mat)
cca_result$cor
```

### Access Canonical Variates

```{r}
can_variates_cp <- cca_result$xcoef
can_variates_sp <- cca_result$ycoef
rho <- cca_result$cor
```

### Test for independence between canonical variate pairs

```{r}
n <- dim(chemical_properties)[1]
p <- dim(chemical_properties)[2]
q <- dim(sensory_properties)[2]

print(n)
print(p)
print(q)
print(rho)
```

```{r}
library(CCP)
```

```{r}
p.asym(rho,n,p,q,tstat = "Wilks")
p.asym(rho,n,p,q,tstat = "Hotelling")
p.asym(rho,n,p,q,tstat = "Pillai")
p.asym(rho,n,p,q,tstat = "Roy")
```

```{r}
Wilks(cancor(cp_mat,sp_mat))
```

### Extract squared canonical correlations

```{r}
squared_cc <- rho^2
squared_cc
```

###  The estimated canonical coefficients

```{r}
cca_result$xcoef
```

```{r}
cca_result$ycoef
```

### Calculate Loadings

```{r}
loadings <- comput(cp_mat,sp_mat,cca_result)
```

```{r}
loadings$corr.X.xscores
```

```{r}
loadings$corr.Y.xscores
```

```{r}
loadings$corr.X.yscores
```

```{r}
loadings$corr.Y.yscores
```

### 
